Temporal Developer Concept Witchery: Latent Dirichlet Allocation Applied to Revisions

### 2009-02-17 lda-paper.tex

\subsection{Extract Repos}
%   2. [ ] Extract Documents
\subsection{Extract Documents}
%   3. [ ] Windowed Sets
\subsection{Windowed Sets}
%   4. [ ] Cluster Windowed Set w/ LDA
\subsection{Cluster Windowed Set w/ LDA}
%   5. [ ] Extract Clusters
\subsection{Extract Clusters}
%   6. [ ] Cluster Similarity [0/1]
\subsection{Cluster Similarity}
%      1. [ ] need the tool
%             grab from the cluster analysis
%   7. [ ] Continuous Cluster Analysis
\subsection{Continuous Cluster Analysis}
%   8. [ ] Topic Smear
\subsection{Topic Smear}
%   9. [ ] Visualization [0/1]
\subsection{Visualization}
%       1. [ ] need the visualizer

>>>>

\subsection{Extract Repos}

We extracted the repositories with software such as rsync, CVSSuck,
\texttt{softChange} and bt2csv.  \texttt{softChange} provided a
general schema for storing revisions. CVSSuck and rsync mirrored CVS
repositories while bt2csv mirrored web accessible bitkeeper
repositories.

%   2. [ ] Extract Documents
\subsection{Extract Documents}
%   3. [ ] Windowed Sets

The document we are primarily using are the changelog comments, these
are the comments added when a revision to the source code is
committed, it could be per file or per commit of changes to multiple
files, this depends on the source control system used.

Documents are converted into word count distributions. The
distributions include all of the possible words in the system.

\subsection{Windowed Sets}

We then create windows which are sets of documents grouped by time
window. Time windows can overlap but don't have to. Windowing by time
allows for many levels of granularity. We usually used one month as
the length of our time windows.

%   4. [ ] Cluster Windowed Set w/ LDA
\subsection{Cluster Windowed Set w/ LDA}
%   5. [ ] Extract Clusters

We take our topic clusterer and cluster the documents by their topics
and get the $n$ unique topic clusters out. In this paper we used LDA
but LSI could be used in a similar way.

This is a very slow step as LDA takes a long time to run.

\subsection{Extract Clusters}

%   6. [ ] Cluster Similarity [0/1]
\subsection{Cluster Similarity}
%      1. [ ] need the tool
%             grab from the cluster analysis
%   7. [ ] Continuous Cluster Analysis

Once we get our clusters, we analyze them and look for repeating
topics. We do this by taking the top 10 most common words and
comparing them. Given a fraction such as 8/10 we joined topics where
8/10 of the top ten topic words were shared.

Clusters in the same period which are this similar are grouped
together. Anything that matches either of those clusters 8/10 will
match.

\subsection{Continuous Cluster Analysis}

We extend the cluster matching across contiguous months.q

%   8. [ ] Topic Smear
\subsection{Topic Smear}
%   9. [ ] Visualization [0/1]
\subsection{Visualization}
%       1. [ ] need the visualizer
